\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

The \emph{SPARQL Query Language for RDF} \cite{W3C-SPARQL1.1-Query-Language-2013} is generally seen as the method of choice to validate RDF data according to certain constraints \cite{Fuerber2010}, 
although, it is not ideal for their formulation. 
In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
Declarative languages may be placed on top of SPARQL and SPIN when using them as implementation languages.
%
The \emph{SPARQL Inferencing Notation (SPIN)} \cite{W3C-SPIN-2011} provides a vocabulary to represent SPARQL queries as RDF triples
and uses SPARQL to specify logical constraints and inference rules \cite{Fuerber2010}.

@@

\emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
\emph{DCMI RDF-AP} uses \emph{DSP} as generic constraint language which is also intuitive for non-experts.
The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.
Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.

>>>>

The \emph{SPARQL Query Language for RDF} \cite{W3C-SPARQL1.1-Query-Language-2013} is generally seen as the method of choice to validate RDF data according to certain constraints \cite{Fuerber2010}, 
although, it is not ideal for their formulation. 
In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
Declarative languages may be placed on top of SPARQL and SPIN when using them as implementation languages. The \emph{SPARQL Inferencing Notation (SPIN)} \cite{W3C-SPIN-2011} provides a vocabulary to represent SPARQL queries as RDF triples
and uses SPARQL to specify logical constraints and inference rules \cite{Fuerber2010}. Kontokostas et al. define 17 data quality integrity constraints represented as SPARQL query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.

@@

The \emph{Dublin Core Application Profile (DCAP)} and \emph{Bibframe} are approaches to specify \emph{profiles} for application-specific purposes. The term \emph{profile} is widely used to refer to a document that describes how standards or specifications are deployed to support the requirements of a particular application, function, community, or context. In the metadata community, the term \emph{application profile} has been applied to describe the tailoring of standards for specific applications. A \emph{Dublin Core Application Profile (DCAP)} \cite{DCMI-DCAP-2009} defines metadata records which meet specific application needs while providing semantic interoperability with other applications on the basis of globally defined vocabularies and models. The \emph{Singapore Framework for Dublin Core Application Profiles} \cite{DCMI-Singapore-2008} is a framework for designing metadata and for defining DCAPs. The framework comprises descriptive components that are necessary or useful for documenting DCAPs.

The \emph{DCMI Abstract Model} \cite{DCMI-Abstract-Model-2007} is required for formalizing a notion of machine-processable application profiles. It specifies an abstract model for Dublin Core metadata which is independent of any particular encoding syntax. Its primary purpose is to specify the components used in Dublin Core metadata. Nilsson et al. \cite{DCMI-DC-RDF-2008} depict how the constructs of the DCMI Abstract Model are represented using the abstract syntax of the RDF model. A \emph{Description Set Profile (DSP)} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile. DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to. The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with DSP.
